Fourmile

### 2022-07-28 fourmile_dataprocess.Rmd
knitted again

library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
```

@@

precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip')

@@

#look at 2011-2013
precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
   scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
  theme_bw() +
  ggtitle('Daily precip')

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
```

@@

precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip (all)')

@@

#look at 2011-2013
precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
   scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
  theme_bw() +
  ggtitle('Daily precip (2011-2013)')
